### 2021-05-24 cued/covid.tex
Covid and risk retro

Please provide details of disrupted project work, including dates when the work was planned to take place and
reasons for the disruption (e.g. inaccessible equipment, illness).
If your work was disrupted, to what extent was it possible to redefine elements of your project so as to achieve
alternative goals? Please comment on the success, or otherwise, of the Covid-19 contingency plan that you
formulated last summer and documented on your Project Planning Form.
This appendix should not exceed one page in length.

>>>>

Thankfully this project was not directly disrupted by Covid-19 as it was always going to be heavily theoretical and computational. The only disruption to speak of was the shift of supervisor meetings to online. Though shared whiteboards were alien at first, we grew to learn how to use them to effectively communicate ideas.

I was ill with Covid-19 for 2 weeks in October but this did not majorly impact my ability to work. The Covid-19 contingency plan formulated last summer and documented on the Project Planning Form just involved switching supervisions to an online format.
